---
title: "The Source of Researcher Variation in Economics"
author: |-
  Nick Huntington-Klein and Claus Pörtner
  
  Seattle University
  
  Please do not share slides until 2024.
format: 
  revealjs:
    theme: serif
editor: visual
execute:
  warning: false
  message: false
  echo: false
---

```{r}
{
  library(rio)
  library(data.table)
  library(ggplot2)
  library(nicksshorts) # remotes::install_github('NickCH-K/nicksshorts')
  library(stringr)
  library(scales)
  library(vtable)
}

dat = import('../Code/cleaned_survey.parquet', setclass = 'data.table')

theme_slides <- theme_nick() + 
  theme(#panel.background = element_rect(fill='transparent'),
        legend.background = element_rect(fill = 'transparent'), #transparent panel bg
    plot.background = element_rect(fill='transparent', color=NA)) #transparent plot bg)
```

## Researcher Degrees of Freedom

the concept\
the entire research pipeline\

## Many-Analyst Studies

background\
small N\
focus on finding variaiton, not explaining it

## The Many-Economists Study

Goal: asking why we differ?\
Approach: do the same replication many times, changing the setting\
Suspected sources: differences over concept of research question, differences in research design, data cleaning, peer interaction\
And what we won't get at: modeling and estimation differences, errors,\
Metrics for comparison: effect size, sign and rejection, sample size, treated and control group sizes, estimation approach\
Not today: use of weights, selection of controls, sample selection choices, qualitative explanations of behavior, potential errors in treatment group definition, language used

## Design

The different stages

## The Replication Task

DACA

## Recruitment and Attrition

recruitment procedures

```{r}
orig_num = dat[is.na(Q2), .N] + uniqueN(dat$Q1)
neverfin = dat[,uniqueN(Q1)]
justcount = dat[!(str_detect(Q2, '\\('))]
justcount = justcount[, .(Participants = uniqueN(Q1)), by = .(Round = Q2)]
justcount = rbind(data.table(Round = c('Original Signup','Assigned Task 1'),
                             Participants = c(orig_num, neverfin)),
                  justcount)
justcount[, Attrition := percent(1-Participants/shift(Participants), .01)]
justcount |> knitr::kable() |>
  kableExtra::kable_styling(font_size = 28)
```

## Education Level Attrition

```{r}
dat[, Researcher_Q10 := as.character(Researcher_Q10)]
dat[Researcher_Q10 == "Professional or graduate degree other than master's or PhD", Researcher_Q10 := 'Prof. Degree']
dat[Researcher_Q10 == "Some graduate school, but no graduate degree", Researcher_Q10 := 'Some Grad School']

fullset = copy(dat)
fullset[is.na(Q1), Q1 := (1:.N) + 100000]

demogdat = dat[Q2 %in% c('The first replication task', 'The third replication task')]
tokeep = c('Q1', names(dat)[names(dat) %like% 'Researcher_'])
tokeep2 = c('Q1', 'Q2', names(dat)[names(dat) %like% 'Researcher_'])
alldemog = rbindlist(list(
  unique(subset(fullset, select = tokeep))[, Q2 := 'Original Signup'],
  unique(subset(dat[!is.na(Q1)], select = tokeep))[, Q2 := 'Assigned Task 1'],
  unique(subset(demogdat, select = tokeep2))
), use.names = TRUE)
qrecode(alldemog, 'Q2',c('Assigned Task 1','Original Signup',
                         'The first replication task',
                         'The third replication task'),
        c('Assigned task 1',
          'Original signup',
          'The first task',
          'The third task'))
alldemog[, Round := factor(Q2, levels = c('Original signup',
                                          'Assigned task 1',
                                          'The first task',
                                          'The third task'))]
alldemog[, Researcher_Q10 := factor(Researcher_Q10,
                                    levels = c('No graduate school',
                                    'Some Grad School',
                                    'Master\'s degree',
                                    'Prof. Degree',
                                    'PhD'))]
qrecode(alldemog, 'Researcher_Q6',
        c('Faculty','Graduate student',
          'Non-faculty researcher at a university', 
          'Other (describe)',
          'Private-sector researcher',
          'Public-sector researcher not at a university'),
        c('Faculty','Grad. Student',
          'Other Researcher','Other','Other Researcher','Other Researcher'))
sumtable(alldemog, vars = 'Researcher_Q10', group = 'Round') |>
  kableExtra::kable_styling(font_size = 28)
```

## Occupation Attrition

```{r}
sumtable(alldemog, vars = 'Researcher_Q6', group = 'Round') |>
  kableExtra::kable_styling(font_size = 28)
```

## Analysis

Basic idea: descriptives of the differences between people, and how they differ (a) through stages, (b) across groups, and (c) based on peer review assignment

Report spread as variance, IQR, and for effect sizes pos/neg/sig/not, and variance weighted by inverse SE, by standard meta-analytic practice

## Effect Sizes

```{r, dev="png", dev.args=list(bg="transparent")}
dat = dat[!is.na(Q2)]
dat = merge(dat, dat[Q2 == 'The third replication task', .(Q1)], by = 'Q1')
qrecode(dat, 'Q2', 
        c('Revision following the first replication task (such as following peer review)',
          'Revision following the second replication task (such as following peer review)',
          'Revision following the third replication task (such as following peer review)',
          'The first replication task',
          'The second replication task',
          'The third replication task'),
        c('Task 1 Revision',
          'Task 2 Revision',
          'Task 3 Revision',
          'Task 1',
          'Task 2',
          'Task 3'), 'Round', checkfrom = TRUE)
dat[, Round := factor(Round, levels = c('Task 1',
                                        'Task 1 Revision',
                                        'Task 2',
                                        'Task 2 Revision',
                                        'Task 3',
                                        'Task 3 Revision'))]
dat[Revision_of_Q4 > 1 & Revision_of_Q6 > 1, Revision_of_Q6 := Revision_of_Q6/100]
dat[Revision_of_Q4 > 1, Revision_of_Q4 := Revision_of_Q4/100]
dat[Revision_of_Q6 < 0, Revision_of_Q6 := abs(Revision_of_Q6)]
viol = dat[Round %in% c('Task 1','Task 2','Task 3') & Revision_of_Q4 != 0, .(Round, Revision_of_Q4, Revision_of_Q6, weight = 1, Type = 'Unweighted')]
viol = rbind(viol,
             dat[Round %in% c('Task 1','Task 2','Task 3'), .(Round, Revision_of_Q4, weight = 1/Revision_of_Q6, Revision_of_Q6, Type = 'Weighted')])
ggplot(viol[!is.infinite(weight)], aes(x = Round, y = Revision_of_Q4, weight = weight)) + 
  geom_violin(fill = 'lightblue', alpha = .5) +
  geom_boxplot(width = .1) +
  geom_hline(yintercept = 0, linetype = 'dashed') +
  theme_slides + 
  coord_cartesian(ylim = c(-.05, .1)) +
  labs(y = 'Effect Size', caption = 'Range limited to [-.05, .1] for viewing.') +
  facet_wrap(~Type, nrow = 2)

```

## Effect Sizes

```{r}
sumtable(viol[!is.infinite(weight) & Type == 'Weighted'], 'Revision_of_Q4', labels = 'Effect Size', group.weights = 'weight', group = 'Round', group.long = TRUE) |>
  kableExtra::kable_styling(font_size = 28)
```

## Effect Sizes

```{r, dev="png", dev.args=list(bg="transparent")}
viol[, ci_upper := Revision_of_Q4 + 1.96*Revision_of_Q6]
viol[, ci_lower := Revision_of_Q4 - 1.96*Revision_of_Q6]
viol[, sig := !xor((ci_upper > 0),(ci_lower > 0))]
setorder(viol, Revision_of_Q4)
viol[, Order := 1:.N, by = .(Round, Type)]
ggplot(viol[Type == 'Unweighted'], aes(x = Order, y = Revision_of_Q4,
                                       ymax = ci_upper, ymin = ci_lower)) + 
  geom_hline(yintercept = 0, linetype = 'dashed') +
  geom_errorbar(mapping = aes(color = sig)) + 
  geom_point()+
  coord_cartesian(ylim = c(-.05, .15)) + 
  scale_color_manual(values = c('lightblue','#ffcccb')) +
  facet_wrap(~Round, nrow = 3) + 
  guides(color = 'none') +
  labs(y = 'Effect Size\n(95% CI)',
       x = NULL, caption = '95% CI reconstructed from effect size and SE,\neven if asymmetric CI was reported. Visible range limited to (-.05, .15).') + 
  theme_slides + 
  theme(axis.text.x = element_blank(),
        axis.ticks.x = element_blank())
```

## Between-Researcher Standard Deviation By Rounds

```{r, dev="png", dev.args=list(bg="transparent")}
byr = dat[Revision_of_Q6 > 0, .(`Standard\nDeviation` = weighted.sd(Revision_of_Q4, 1/Revision_of_Q6, na.rm = TRUE), N = .N), by = Round]
setorder(byr, Round)
byr[, ID := 1:.N]
dat[, demean := (Revision_of_Q4 - mean(Revision_of_Q4, na.rm = TRUE))^2, by = Round]
m = lm(demean ~ as.numeric(Round), data = dat[Revision_of_Q6 >0 & as.numeric(Round) %in% c(1,3,5)], weights = 1/dat[Revision_of_Q6 > 0 & as.numeric(Round) %in% c(1,3,5), Revision_of_Q6])
ggplot(byr, aes(x = ID, y = `Standard\nDeviation`, label = paste0(number(`Standard\nDeviation`, .001),'\n(N=',number(N),')'))) + 
  geom_line() + 
  geom_point(color = 'lightblue', size = 3) + 
  geom_text(family = 'serif', size = 12/.pt, vjust = -1) +
  scale_x_continuous(labels = byr$Round) + 
  expand_limits(y = c(min(byr$`Standard\nDeviation`)*.8,max(byr$`Standard\nDeviation`)*1.2)) +
  theme_slides + 
  labs(x = NULL)
```

## Peer Review

Show change in overall variance from stage to stage, and also show whether peer review pairs become more similar after their review (abs. difference in effect)

Also see whether stage-to-stage variance is different between those assigned to peer review *at all* vs those who weren't

```{r, dev="png", dev.args=list(bg="transparent")}
compare_revis = function(r) {
  thisr = dat[Round %in% paste0('Task ', r, c('',' Revision'))]
  pairs = fread(paste0('../code/task_',r,'_peer_review_pairs.csv'))
  pairs = pairs[!(dont_send)]
  thisr = merge(thisr, pairs[, .(Q1 = id2, match = id1, pairID)], all.x = TRUE)
  thisr[, got_reviewed := !is.na(pairID)]
  thisr[, Stage := fifelse(Round == paste0('Task ', r), 0, 1)]
  thisr[, ReviewRound := r]
  return(thisr)
}
reviews = rbindlist(lapply(1:3, compare_revis))

# Find differences in other rounds
get_diff = function(i, r) {
  if (!reviews[i, got_reviewed]) {
    return(NA_real_)
  }
  thispair = reviews[Q1 %in% c(reviews[i, Q1], reviews[i, match]) & Round == r]
  if (nrow(thispair) < 2) {
    return(NA_real_)
  }
  return(abs(thispair$Revision_of_Q4[2] - thispair$Revision_of_Q4[1]))
}

roundnames = sort(unique(reviews$Round))
for (rn in 1:length(roundnames)) {
  reviews[[paste0('Diff_',rn)]] = sapply(1:nrow(reviews), \(x) get_diff(x, roundnames[rn]))
}

# for now
reviews$Diff_6 = NA_real_

more_sim = unique(reviews[Stage == 0 & (got_reviewed), .(Round, pairID, Diff_1, Diff_2, Diff_3, Diff_4, Diff_5, Diff_6)])

reviews[, Reviewed_1 := fifelse(sum(ReviewRound == 1) > 0, any(got_reviewed[ReviewRound == 1]), FALSE), by = Q1]
reviews[, Reviewed_2 := fifelse(sum(ReviewRound == 2) > 0, any(got_reviewed[ReviewRound == 2]), FALSE), by = Q1]
reviews[, Reviewed_3 := fifelse(sum(ReviewRound == 3) > 0, any(got_reviewed[ReviewRound == 3]), FALSE), by = Q1]

dist_compare = rbindlist(list(
  reviews[Round == 'Task 1' & Revision_of_Q6 > 0, .(Round = 'Round 1', Reviewed = Reviewed_1, Observed = 'Pre-Review', Effect = Revision_of_Q4, weight = 1/Revision_of_Q6)],
  reviews[Round == 'Task 2' & Revision_of_Q6 > 0, .(Round = 'Round 1', Reviewed = Reviewed_1, Observed = 'Next Round', Effect = Revision_of_Q4, weight = 1/Revision_of_Q6)],
  reviews[Round == 'Task 2' & Revision_of_Q6 > 0, .(Round = 'Round 2', Reviewed = Reviewed_2, Observed = 'Pre-Review', Effect = Revision_of_Q4, weight = 1/Revision_of_Q6)],
  reviews[Round == 'Task 3' & Revision_of_Q6 > 0, .(Round = 'Round 2', Reviewed = Reviewed_2, Observed = 'Next Round', Effect = Revision_of_Q4, weight = 1/Revision_of_Q6)]
))
dist_compare[, Observed := factor(Observed, levels = c('Pre-Review','Next Round'))]
dist_compare[, Reviewed := fifelse(Reviewed == 1, 'Not Peer-Reviewed','Peer Reviewed')]
ggplot(dist_compare, aes(x = Effect, weight = weight, color = Reviewed, fill = Reviewed)) + 
  geom_density(alpha = .4) + 
  coord_cartesian(xlim = c(-.05, .15)) + 
  facet_grid(cols = vars(Observed), rows = vars(Round)) + 
  theme_slides + 
  labs(caption = 'Viewing range limited to .05 to .15.', y = 'Density')
```

## Do You Become More Like Your Reviewer?

```{r, dev="png", dev.args=list(bg="transparent")}
reviews = rbindlist(lapply(1:3, compare_revis))

# Find differences in other rounds
get_diff_across = function(i, r) {
  if (!reviews[i, got_reviewed]) {
    return(NA_real_)
  }
  thispair = reviews[(Q1 == reviews[i, Q1] & Round == r) | (Q1 == reviews[i, match] & Round == paste0('Task ', as.numeric(str_sub(r,-1))-1))]
  if (nrow(thispair) < 2) {
    return(NA_real_)
  }
  return(abs(thispair$Revision_of_Q4[2] - thispair$Revision_of_Q4[1]))
}

roundnames = c('Task 1','Task 2','Task 3')
for (rn in 1:length(roundnames)) {
  reviews[[paste0('Diff_',rn)]] = sapply(1:nrow(reviews), \(x) get_diff(x, roundnames[rn]))
  reviews[[paste0('Diff_',rn,'_vs_',rn-1)]] = sapply(1:nrow(reviews), \(x) get_diff_across(x, roundnames[rn]))
}

# for now
reviews$Diff_6 = NA_real_

unreviewed = reviews[!(got_reviewed)]
reviews = reviews[(got_reviewed)]

unreviewed[, id := 1:.N]
allreviews = CJ(id1 = 1:nrow(unreviewed), id2 = 1:nrow(unreviewed))
allreviews = allreviews[id1 != id2]
ar_round1 = merge(allreviews, unreviewed[Round == 'Task 1', .(id1 = id, E1 = Revision_of_Q4)], by = 'id1')
ar_round1 = merge(ar_round1, unreviewed[Round == 'Task 1', .(id2 = id, E2 = Revision_of_Q4)], by = 'id2')
ar_round1[, diff := abs(E1-E2)]
ar_round2 = merge(allreviews, unreviewed[Round == 'Task 2', .(id1 = id, E1 = Revision_of_Q4)], by = 'id1')
ar_round2 = merge(ar_round2, unreviewed[Round == 'Task 2', .(id2 = id, E2 = Revision_of_Q4)], by = 'id2')
ar_round2[, diff := abs(E1-E2)]
ar_round3 = merge(allreviews, unreviewed[Round == 'Task 3', .(id1 = id, E1 = Revision_of_Q4)], by = 'id1')
ar_round3 = merge(ar_round3, unreviewed[Round == 'Task 3', .(id2 = id, E2 = Revision_of_Q4)], by = 'id2')
ar_round3[, diff := abs(E1-E2)]
ar_round2v1 = merge(allreviews, unreviewed[Round == 'Task 1', .(id1 = id, E1 = Revision_of_Q4)], by = 'id1')
ar_round2v1 = merge(ar_round2v1, unreviewed[Round == 'Task 2', .(id2 = id, E2 = Revision_of_Q4)], by = 'id2')
ar_round2v1[, diff := abs(E1-E2)]
ar_round3v2 = merge(allreviews, unreviewed[Round == 'Task 2', .(id1 = id, E1 = Revision_of_Q4)], by = 'id1')
ar_round3v2 = merge(ar_round3v2, unreviewed[Round == 'Task 3', .(id2 = id, E2 = Revision_of_Q4)], by = 'id2')
ar_round3v2[, diff := abs(E1-E2)]

changediff = rbindlist(list(
  data.table(Type = 'Reviewed',Round = 'Task 1', Comparison = 'Original',
             diff = reviews[Round == 'Task 1', Diff_1]),
  data.table(Type = 'Reviewed',Round = 'Task 1', Comparison = 'Next Round', 
             diff = reviews[Round == 'Task 1', Diff_2]),
  data.table(Type = 'Reviewed',Round = 'Task 1', Comparison = 'Next vs. This',
            diff = reviews[Round == 'Task 1', Diff_2_vs_1]),
  data.table(Type = 'Reviewed',Round = 'Task 2', Comparison = 'Original',
           diff = reviews[Round == 'Task 2', Diff_2]),
  data.table(Type = 'Reviewed',Round = 'Task 2', Comparison = 'Next Round',
           diff = reviews[Round == 'Task 2', Diff_3]),
  data.table(Type = 'Reviewed',Round = 'Task 2', Comparison = 'Next vs. This',
           diff = reviews[Round == 'Task 2', Diff_3_vs_2]),
  data.table(Type = 'Unreviewed', Round = 'Task 1', Comparison = 'Original',
             diff = ar_round1$diff),
  data.table(Type = 'Unreviewed', Round = 'Task 2', Comparison = 'Original',
             diff = ar_round2$diff),
  data.table(Type = 'Unreviewed', Round = 'Task 1', Comparison = 'Next Round',
             diff = ar_round2$diff),
  data.table(Type = 'Unreviewed', Round = 'Task 2', Comparison = 'Next Round',
             diff = ar_round3$diff),
  data.table(Type = 'Unreviewed', Round = 'Task 1', Comparison = 'Next vs. This',
             diff = ar_round2v1$diff),
    data.table(Type = 'Unreviewed', Round = 'Task 2', Comparison = 'Next vs. This',
             diff = ar_round3v2$diff)
))
changediff[, Comparison := factor(Comparison, levels = c('Original','Next Round','Next vs. This'))]
ggplot(changediff, aes(x = Comparison, y = diff, color = Type)) + 
  geom_violin() + 
  geom_boxplot(width = .2, position = position_dodge(.9))  + 
  coord_cartesian(ylim = c(0, .1)) + 
  theme_slides + 
  facet_wrap(~Round, nrow = 2) + 
  labs(caption = str_wrap('For Task 1, Original is Task 1 effect vs. Task 1 partner\'s Task 1, Next Round is Task 2 effect vs. Task 1 partner\'s Task 2, and Next Vs. This is Task 2 effect vs. Task 1 partner\'s Task 1', 100),
       y = 'Absolute\neffect\ndifference')
```

## Changes in Peer Similarity

```{r}
feols(diff ~ Comparison*Type, data = changediff, split = 'Round') |> 
  modelsummary::msummary(stars = c('*' = .1, '**' = .05, '***' = .01),
                         gof_omit = c('IC|R2|RMSE|Err'))
```

## Sample Sizes

Repeat the effect size analyses, except the ones requiring a standard error

```{r, dev="png", dev.args=list(bg="transparent")}
viol = dat[Round %in% c('Task 1','Task 2','Task 3'), .(Round, Revision_of_Q12, Revision_of_Q18, Revision_of_Q21)]
ggplot(viol, aes(x = Round, y = Revision_of_Q12)) + 
  geom_violin(fill = 'lightblue', alpha = .5, scale = 'width') +
  geom_boxplot(width = .1) +
  theme_slides + 
  scale_y_log10(labels = label_rangescale()) +
  labs(y = 'Sample\nSize')


```

## Treated Group Sample Sizes

```{r, dev="png", dev.args=list(bg="transparent")}
ggplot(viol, aes(x = Round, y = Revision_of_Q18)) + 
  geom_violin(fill = 'lightblue', alpha = .5, scale = 'width') +
  geom_boxplot(width = .1) +
  theme_slides + 
  scale_y_log10(labels = label_rangescale()) +
  labs(y = 'Treated\nGroup\nSample\nSize')
```

## Untreated Group Sample Sizes

```{r, dev="png", dev.args=list(bg="transparent")}
ggplot(viol, aes(x = Round, y = Revision_of_Q21)) + 
  geom_violin(fill = 'lightblue', alpha = .5, scale = 'width') +
  geom_boxplot(width = .1) +
  theme_slides + 
  scale_y_log10(labels = label_rangescale()) +
  labs(y = 'Untreated\nGroup\nSample\nSize')
```

## Sample Size Summaries

```{r}
sumtable(viol, c('Revision_of_Q12','Revision_of_Q18','Revision_of_Q21'), labels = c('Overall Sample','Treated','Untreated'), group = 'Round', group.long = TRUE, numformat = 'comma') |>
  kableExtra::kable_styling(font_size = 24)
```

## Analytic Choices

Show distribution of e.g. logit/linear, standard error adjustments across stages

## Researcher Characteristics

Not really powered!

Calculate absolute difference from mean (median?) of effect size and also sample size. Regress abs difference on different researcher characteristics one at a time

## Conclusion

Where did we seem to see increasing agreement?

What changes in practice would make research results more consistent?

Do we want consistency?
